2-factor-Hull-White\_model\_calibration

### 2020-04-26 week5/Report.tex
Report Body Finished

\section{Introduction
}
We initialize most variables as given by the question.

\begin{itemize}
    \item Option maturity is one year
    \item The option is struck at-the-money
    \item The current share price is \$100
    \item The risk-free continuously compounded interest rate is 8%
    \item The volatility for the underlying share is 30%
\end{itemize}

@@

\section{Simulate a share price path using CEV Model
}

@@

>>>>

\section{Introduction
}

In this paper we go beyond the constant volatility assumption in the Black-Scholes model.  Most of code implemented in this submission id derived from Moldule 5 \cite{M5} of the course.

We initialize most variables as given by the question.

\begin{itemize}
    \item Option maturity is one year
    \item The option is struck at-the-money
    \item The current share price is \$100
    \item The risk-free continuously compounded interest rate is 8\%
    \item The volatility for the underlying share is 30\%
\end{itemize}

@@

\section{Simulate a share price path using CEV Model
}
Cox \cite{Cox1} developed the constant elasticity of variance (CEV) option pricing model, it attempts to capture stochastic volatility and is given by:

\[dS_t =  \mu S_t dt + \sigma  S^\gamma _t dW_t\]

If $\gamma = 1$ this model return the same value as Black-Scholes model, however if the value of $\gamma < 1 $ we experience an effect called leverage effect where the volatility increases as the price decreases over subsequent time periods.

Based on the assumption that $\sigma(t_i,t_{i+1}) = \sigma(S_{ti})^{\gamma-1}$, where $\sigma = 0.3$ and $\gamma = 0.75$.  We can simulate the next step in a share price path using the following formula:
$$S_{t_{i+1}} = S_{t_i}e^{(r - \frac{\sigma^2 (t_i,t_{i+1})}{2})(t_{i+1}-t_i)+\sigma(t_i, t_{i+1})\sqrt{t_{i+1}-t_i}Z}$$
where $S_{ti}$ is the share price at time $t_i$, $\sigma(t_i, t_{i+1})$ is the volatility for the period $[t_i,t_{i+1}]$, r is the risk-free interest rate, and Z~N(0, 1)

First, we define our helper functions. The next\_share\_price function
is used to calculate the evolution of the share price at t+1, from the
share price at t. We generate the random variable Z from within this
function. The effective sigma is also written as a function of the share
price at t.

Just for exploration purposes, we also added a varying\_vol flag, to
allow us to switch between a constant volatility and varying volatility.
We use the initial stock price instead of the previous price when
assuming a contant volatility.

The other function is the generate\_share\_price\_path function. We
first create an empty numpy array of shape (sample\_size x timesteps+1).
Note the addition of one element to the timestep, as the first element
is equal to the initial stock price. We then iterate through each path,
and each timestep, applying the next\_share\_price function against the
previous share price. We then convert the result into a pandas DataFrame
and return the results.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{7}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{dT}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
    \PY{n}{Z} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size}\PY{o}{=}\PY{n}{sample\PYZus{}size}\PY{p}{)}
    \PY{k}{if} \PY{n}{varying\PYZus{}vol}\PY{p}{:}
        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{prev\PYZus{}price}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}
    \PY{k}{else}\PY{p}{:}
        \PY{n}{sigma} \PY{o}{=} \PY{n}{sigma\PYZus{}const}\PY{o}{*}\PY{p}{(}\PY{n}{S0}\PY{p}{)}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{n}{gamma}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}

    \PY{k}{return} \PY{n}{prev\PYZus{}price}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{p}{(}\PY{n}{r}\PY{o}{\PYZhy{}}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{+}\PY{p}{(}\PY{n}{sigma}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol} \PY{o}{=} \PY{k+kc}{True}\PY{p}{)}\PY{p}{:}
    \PY{n}{df} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{p}{[}\PY{n}{S0}\PY{p}{]}\PY{o}{*}\PY{n}{sample\PYZus{}size}\PY{p}{)}
    \PY{k}{for} \PY{n}{t} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{timesteps}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{:}
        \PY{n}{df}\PY{p}{[}\PY{n}{t}\PY{p}{]} \PY{o}{=} \PY{n}{next\PYZus{}share\PYZus{}price}\PY{p}{(}\PY{n}{df}\PY{p}{[}\PY{n}{t}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{p}{)}
    \PY{k}{return} \PY{n}{df}\PY{o}{.}\PY{n}{T}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{8}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{patches} \PY{k}{as} \PY{n+nn}{mpatches}
\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{10}
\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}

\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}cev} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{)}
\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}black\PYZus{}scholes} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{l+m+mf}{1.0}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}

\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}cev}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{red}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}path\PYZus{}black\PYZus{}scholes}\PY{p}{,} \PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Timestep}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Share price}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{red\PYZus{}patch} \PY{o}{=} \PY{n}{mpatches}\PY{o}{.}\PY{n}{Patch}\PY{p}{(}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{red}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CEV}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{blue\PYZus{}patch} \PY{o}{=} \PY{n}{mpatches}\PY{o}{.}\PY{n}{Patch}\PY{p}{(}\PY{n}{color}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blue}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{BSM}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{n}{handles}\PY{o}{=}\PY{p}{[}\PY{n}{red\PYZus{}patch}\PY{p}{,} \PY{n}{blue\PYZus{}patch}\PY{p}{]}\PY{p}{,} \PY{n}{loc}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{upper left}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{CEV vs BSM Stock Price Paths}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_17_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Next, we create a python dictionary called share\_price\_paths, to hold
our results for part 2. The key of this dictionary would be the number
of sample price paths, while the values would be the dataframes
containing the price paths. We also track the rough processing time
required at each step, by printing the time when each iteration
completes.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{9}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{time}

\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1}
\PY{n}{sample\PYZus{}sizes} \PY{o}{=} \PY{n+nb}{range}\PY{p}{(}\PY{l+m+mi}{1000}\PY{p}{,} \PY{l+m+mi}{50001}\PY{p}{,} \PY{l+m+mi}{1000}\PY{p}{)}

\PY{n}{share\PYZus{}price\PYZus{}paths} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}

\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Start generating share price path}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\PY{n}{start} \PY{o}{=} \PY{n}{time}\PY{o}{.}\PY{n}{time}\PY{p}{(}\PY{p}{)}
\PY{k}{for} \PY{n}{sample\PYZus{}size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
    \PY{n}{share\PYZus{}val} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}price\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{r}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sigma\PYZus{}const}\PY{p}{,} \PY{n}{gamma}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps}\PY{p}{,} \PY{n}{varying\PYZus{}vol}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}

    \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]} \PY{o}{=} \PY{n}{share\PYZus{}val}
    \PY{c+c1}{\PYZsh{}print(\PYZdq{}Updated for sample size \PYZob{}\PYZcb{} at \PYZob{}\PYZcb{}\PYZdq{}.format(sample\PYZus{}size, datetime.datetime.now().strftime(\PYZsq{}\PYZpc{}H:\PYZpc{}M\PYZsq{})))}
\PY{n}{end} \PY{o}{=} \PY{n}{time}\PY{o}{.}\PY{n}{time}\PY{p}{(}\PY{p}{)}
\PY{n+nb}{print}\PY{p}{(}\PY{l+s+sa}{f}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{Generating all samples paths takes }\PY{l+s+s2}{\PYZob{}}\PY{l+s+s2}{(end \PYZhy{} start):.2f\PYZcb{}s}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
Start generating share price path
Generating all samples paths takes 2.58s
    \end{Verbatim}

    To display our output, we show the first 10 price paths generated by our
iteration with 1000 samples:

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{10}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{p}{:}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{:}\PY{l+m+mi}{10}\PY{p}{]}
\end{Verbatim}
\end{tcolorbox}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{10}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
             0           1           2           3           4           5  \textbackslash{}
0   100.000000  100.000000  100.000000  100.000000  100.000000  100.000000
1    99.626771   99.374526  100.689569   97.065445  106.862386   99.918343
2   103.745565   96.967926  102.622183   96.451414  106.332275   96.640428
3   107.154631   96.585243  105.974778   93.207852  100.177288   99.129417
4   111.716818   95.838855  101.540594   94.146336   98.646601  102.592136
5   120.620494   93.477848  100.930914   94.502805  100.662067  103.175996
6   122.217586   87.674152  101.799340   91.076602  101.876289  102.336328
7   123.138256   87.108925  103.904210   94.061221  106.060742  103.426255
8   129.359695   87.871374  100.925245   92.948402  115.010833   98.206543
9   123.575048   87.571414  105.883449   95.799071  117.769685   97.640631
10  125.486476   88.836040  104.337774   96.829970  119.866089  100.623917
11  124.538067   92.114326  106.173600   98.493852  118.497793   99.093147
12  123.548415   92.619346  104.478810   98.081928  114.719969   94.669329

             6           7           8           9
0   100.000000  100.000000  100.000000  100.000000
1   106.483031  100.796117  100.030802  102.593647
2   105.512423  101.627748   98.448810  103.179244
3   107.821291   98.518154   97.598741  103.563761
4   108.394844   97.918995   99.489053  110.865271
5   108.425203   99.326116   97.269739  108.916593
6   107.844372  103.199284   98.432527  108.089622
7   108.269775  100.286497  101.084604  107.860547
8   108.268731   99.113198  101.552266  103.792957
9   103.400905   98.076554  100.633537  106.623775
10  107.548810   98.062335   97.583078  110.004438
11  104.394412   98.481303   94.325492  107.980799
12  103.306627   95.171645   94.012006  108.960908
\end{Verbatim}
\end{tcolorbox}

    Next, we plot the price paths for the iteration with 1000 samples,

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{l+m+mi}{1000}\PY{p}{]}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{xlabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Timestep}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{ylabel}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Share price}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Sample of 1000 Share Price Paths}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_23_0.png}
    \end{center}
    { \hspace*{\fill} \\}

@@

    Using Monte Carlo, we calculate the price of the vanilla call option as
follows:

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{12}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{price\PYZus{}estimate} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{n}{price\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}

\PY{k}{for} \PY{n}{size} \PY{o+ow}{in} \PY{n}{sample\PYZus{}sizes}\PY{p}{:}
    \PY{n}{S\PYZus{}Ts} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{p}{[}\PY{n}{size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{l+m+mi}{12}\PY{p}{,} \PY{p}{:}\PY{p}{]}
    \PY{n}{payoff} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{S\PYZus{}Ts} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
    \PY{n}{discounted\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoff}
    \PY{n}{price\PYZus{}estimate}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{discounted\PYZus{}price}\PY{o}{.}\PY{n}{mean}\PY{p}{(}\PY{p}{)}\PY{p}{)}
    \PY{n}{price\PYZus{}std}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{discounted\PYZus{}price}\PY{o}{.}\PY{n}{std}\PY{p}{(}\PY{p}{)}\PY{o}{/}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{size}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{13}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{The price estimated by Monte Carlo when using sample size of 50,000 is : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{price\PYZus{}estimate}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{)}\PY{p}{)} 
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
The price estimated by Monte Carlo when using sample size of 50,000 is : 8.694
    \end{Verbatim}

We then compare with calculation of CEV model using noncentralchi-squared

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{14}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k}{as} \PY{n+nn}{np}
\PY{k+kn}{import} \PY{n+nn}{matplotlib}\PY{n+nn}{.}\PY{n+nn}{pyplot} \PY{k}{as} \PY{n+nn}{plt}
\PY{k+kn}{from} \PY{n+nn}{scipy}\PY{n+nn}{.}\PY{n+nn}{stats} \PY{k+kn}{import} \PY{n}{ncx2}

\PY{n}{S0} \PY{o}{=} \PY{l+m+mi}{100}
\PY{n}{sigma} \PY{o}{=} \PY{l+m+mf}{0.3}
\PY{n}{gamma} \PY{o}{=} \PY{l+m+mf}{0.75}
\PY{n}{r} \PY{o}{=} \PY{l+m+mf}{0.08}
\PY{n}{T} \PY{o}{=} \PY{l+m+mi}{1}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{15}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{z} \PY{o}{=} \PY{l+m+mi}{2} \PY{o}{+} \PY{l+m+mi}{1}\PY{o}{/}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}
\PY{k}{def} \PY{n+nf}{C}\PY{p}{(}\PY{n}{t}\PY{p}{,}\PY{n}{K}\PY{p}{)}\PY{p}{:}
    \PY{n}{kappa} \PY{o}{=} \PY{l+m+mi}{2}\PY{o}{*}\PY{n}{r}\PY{o}{/}\PY{p}{(}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{o}{*}\PY{n}{t}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
    \PY{n}{x} \PY{o}{=} \PY{n}{kappa}\PY{o}{*}\PY{n}{S0}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{p}{)}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{n}{r}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{o}{*}\PY{n}{t}\PY{p}{)}
    \PY{n}{y} \PY{o}{=} \PY{n}{kappa}\PY{o}{*}\PY{n}{K}\PY{o}{*}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{2}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{gamma}\PY{p}{)}\PY{p}{)}
    \PY{k}{return} \PY{n}{S0}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{ncx2}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{y}\PY{p}{,}\PY{n}{z}\PY{p}{,}\PY{n}{x}\PY{p}{)}\PY{p}{)}\PY{o}{\PYZhy{}}\PY{n}{K}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{r}\PY{o}{*}\PY{n}{t}\PY{p}{)}\PY{o}{*}\PY{n}{ncx2}\PY{o}{.}\PY{n}{cdf}\PY{p}{(}\PY{n}{x}\PY{p}{,}\PY{n}{z}\PY{o}{\PYZhy{}}\PY{l+m+mi}{2}\PY{p}{,}\PY{n}{y}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{16}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{cev\PYZus{}call\PYZus{}price} \PY{o}{=} \PY{n}{C}\PY{p}{(}\PY{n}{T}\PY{p}{,} \PY{l+m+mi}{100}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{17}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n+nb}{print}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{The price calculated via CEV model using noncentral chi\PYZhy{}squared distribution is : }\PY{l+s+si}{\PYZob{}:.3f\PYZcb{}}\PY{l+s+s2}{\PYZdq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n}{cev\PYZus{}call\PYZus{}price}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
The price calculated via CEV model using noncentral chi-squared distribution is
: 8.702
    \end{Verbatim}

    We plot the prices of our Monte Carlo estimates against the CEV
noncentral chi-squared distribution prices calculated from Part 1 above:

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{18}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{p}{[}\PY{n}{cev\PYZus{}call\PYZus{}price}\PY{p}{]}\PY{o}{*}\PY{l+m+mi}{50}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CEV Call Price}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{.}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{label}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Monte Carlo Estimates}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{+} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{plot}\PY{p}{(}\PY{n}{price\PYZus{}estimate} \PY{o}{\PYZhy{}} \PY{l+m+mi}{3}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{n}{price\PYZus{}std}\PY{p}{)}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{r}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{legend}\PY{p}{(}\PY{p}{)}
\PY{n}{plt}\PY{o}{.}\PY{n}{show}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_35_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    We also plot the prices of our Monte Carlo estimates against the Fourier
Call prices calculated from Part 1 above:
